|

### 2016-06-23 Manuals/PrideID/Manual-PrideID.Rmd
archive

```{r, warning=FALSE, echo=FALSE, include=FALSE, cache=F}
setwd("~/Dropbox/_SPACE/Benchmark/11copy")
file_mzid        <- list.files(path = ".", pattern ="mzid", all.files = F, 
                      full.names = F, recursive = F, ignore.case = T, include.dirs = F)
file_mzml        <- list.files(path = ".", pattern ="mzML$|mzXML$", all.files = F, 
                      full.names = F, recursive = F, ignore.case = T, include.dirs = F)
file_fasta        <- list.files(path = ".", pattern ="fasta", all.files = F, 
                      full.names = F, recursive = F, ignore.case = T, include.dirs = F)

@@

```{r echo=F, cache=T, warning=F, include=F}
setwd("~/Dropbox/_SPACE/Benchmark/11copy")
dta_mzid  <- mzID(file="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_dta.mzid")
#dta_mzml  <- readMSData(files = file_mzml[2])
#dta       <- read.table("TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_dta.tsv", sep="\t", header = T)
dta_flt    <- flatten(dta_mzid)
colnames(dta_flt)[2] <- "Scan"

@@

```{r, echo=F}
setwd("~/Dropbox/_SPACE/Benchmark/11copy")
q_pnnl <- read.table(file="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_ReporterIons.txt",sep="\t", header = T)
names(q_pnnl)[2] <- "Scan"
q_merge <- merge(frm_docker[,c("Scan","Spec_Evalue", "iTRAQ4.114", "iTRAQ4.115", "iTRAQ4.116", "iTRAQ4.117")], y=q_pnnl[,c("Scan","Ion_114","Ion_115","Ion_116","Ion_117")], by="Scan")

>>>>

```{r, warning=FALSE, echo=FALSE, include=FALSE, cache=F}
setwd("~/Desktop/11copy")
file_mzid        <- list.files(path = ".", pattern ="mzid", all.files = F, 
                      full.names = F, recursive = F, ignore.case = T, include.dirs = F)
file_mzml        <- list.files(path = ".", pattern ="mzML$|mzXML$", all.files = F, 
                      full.names = F, recursive = F, ignore.case = T, include.dirs = F)
file_fasta        <- list.files(path = ".", pattern ="fasta", all.files = F, 
                      full.names = F, recursive = F, ignore.case = T, include.dirs = F)

@@

```{r echo=F, cache=T, warning=F, include=F}
setwd("~/Desktop/11copy")
dta_mzid  <- mzID(file="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_dta.mzid")
#dta_mzml  <- readMSData(files = file_mzml[2])
#dta       <- read.table("TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_dta.tsv", sep="\t", header = T)
dta_flt    <- flatten(dta_mzid)
colnames(dta_flt)[2] <- "Scan"

@@

```{r, echo=F}
setwd("~/Desktop/11copy")
q_pnnl <- read.table(file="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_ReporterIons.txt",sep="\t", header = T)
names(q_pnnl)[2] <- "Scan"
q_merge <- merge(frm_docker[,c("Scan","Spec_Evalue", "iTRAQ4.114", "iTRAQ4.115", "iTRAQ4.116", "iTRAQ4.117")], y=q_pnnl[,c("Scan","Ion_114","Ion_115","Ion_116","Ion_117")], by="Scan")
